\begin{thebibliography}{9}

\bibitem {batesroo2000} \textsc{Bates P. D., De Roo A. P. J. } , \textit{A simple raster-based model for flood inundation simulation.},   J. Hydrol. 236. 2000.

\bibitem {Bekkar2013} \textsc{Bekkar M., Djemaa H. K., Alitouche T. A.} , \textit{Evaluation Measures for Models Assessment over Imbalanced Data Sets}, Journal of Information Engineering and Applications, Vol.3, No.10

\bibitem {Puyol2006} \textsc{Breña Puyol, A. F., Jacobo Villa, M. A.} , \textit{Principios y Fundamentos de la Hidrología Superficial.} Universidad Autónoma Metropolitana de México, 2006.


\bibitem {Puyol2006} \textsc{Brodersen K. H., Ong C. S., Stephan, K. E., Buhmann, J. M.} , \textit{The balanced accuracy and its posterior distribution.} Universidad Autónoma Metropolitana de México, 2006.

\bibitem {burgosINA} \textsc{Burgos, V. H.} , \textit{Evaluación de ASTER GDEM y SRTM-C/X para modelación hidráulica de la rotura de presa El Carrizal, Mendoza}, Department of Computer Science, ETH Zurich, Suiza. 2010

\bibitem {Byoung2015} \textsc{Byoung C. K., Hyeong H. K., Jae Y. N.} , \textit{Classification of Potential Water Bodies Using Landsat 8 OLI and a Combination of Two Boosted Random Forest Classifiers}, Sensors (Basel), pp. 13763–13777, 2015

\bibitem {Carignano2014} \textsc{Carignano, C. A., Krohling D., Degiovanni, S., Cioccale, M. A.} , \textit{Relatorio del XIX Congreso Geológico Argentino - Córdoba} XIX Congreso Geológico Argentino. 2014

\bibitem {Chuvieco1996} \textsc{Chuvieco E.} , \textit{Fundamentos de Teledetección Espacial 3rd ed.} 568pp. 1996

\bibitem {diaz2010} \textsc{Díaz, G. M., Gómez, M., Deccechis, F., Lencinas, J.D.,del Valle, H.F.} , \textit{Evaluación de los modelos digitales de elevación SRTM-C/X y ASTER GDEM y su relación con los errores planimétricos de datos pancromáticos Quickbird ortorrectificados}, Laboratorio de Percepción Remota y SIG. Centro de Investigación y Extensión Forestal Andino Patagónico (CIEFAP). 2010

\bibitem {farr2000} \textsc{Farr, T.G., Kobrick, M.} , \textit{Shuttle Radar Topography Mission produces a wealth of data}, Amer. Geophys. Union Eos, v. 81, p. 583-585. 2000.

\bibitem {farr2007} \textsc{Farr, T. G., Rosen, P. A., Caro, E., Crippen, R., Duren, R., Hensley, S., Kobrick, M., Paller, M., Rodriguez, E., Roth, L., Seal, D., Shaffer, S., Shimada, J., Umland, J., Werner, M., Oskin, M., Burbank, D., Alsdorf, D.,} , \textit{The Shuttle Radar Topography Mission}, Reviews of Geophysics, American Geophysical Union, 2007.


\bibitem {Ferpozzi1988} \textsc{Ferpozzi, L.} , \textit{Principales rasgos geomorfológicos y dinámica hídrica de un sector de la llanura sudoriental de la Provincia de Córdoba} , República Argentina. 2º Simposio Latinoamericano sobre Sensores Remotos, Actas. p. 23. Bogotá. 1988

\bibitem {forkuor2012} \textsc{Forkuor, G., Maathuis, B.H.P.} , \textit{Comparison of SRTM and ASTER Derived Digital Elevation Models over Two Regions in Ghana - Implications for Hydrological and Environmental Modeling}, Studies on Environmental and Applied Geomorphology. 2012

\bibitem {gaobc} \textsc{Gao BC.} , \textit{NDWI — A normalized difference water index for remote sensing of vegetation liquid water from space.}, Remote Sens Environ. 58:257–266. 1996

\bibitem {gonzalez1993} \textsc{González, R., Wood, R.} , \textit{Digital Image Processing}, Addison-Wesley Publishing Company, Inc.

\bibitem {guerrero2013} \textsc{Guerrero Cordova, C. G.} , \textit{Reingeniería de Simulador Hidrológico Orientado al Análisis Predictico de Inundaciones}, Universidad Nacional de Córdoba - Argentina. 2013

\bibitem {Iriondo2007} \textsc{Iriondo, M., Kröhling, D.} , \textit{Geomorfología y Sedimentología de la Cuenca Superior del Río Salado (Sur de Santa Fe y Noroeste de Buenos Aires, Argentina).} Latin American Journal of Sedimentology and Basin Analysis 14: 1–23. 2007

\bibitem {Iriondo2008} \textsc{Iriondo, M., Brunetto, E.} , \textit{El Mar de Arena Pampeano en el sudeste de Córdoba. 17º Congreso Geológico Argentino} Actas: 1224–1225. Jujuy.

\bibitem {Iriondo2011} \textsc{Iriondo, M., Kröhling, D., Brunetto, E.} , \textit{Aridization, dune dissipation and pedogenesis in the Quaternary of Eastern Pampean Sand Sea.} En Murphy, J. (ed.) Sand Dunes: Conservation, Shapes/Types and Desertification. Nova Science Publishers, Inc. 1–42. USA. Universidad Autónoma Metropolitana de México, 2011

\bibitem {Kiamehr2005} \textsc{Kiamehr, R., Sjoberg, L.E.} , \textit{Effect of the SRTM global DEM on the determination of a highresolution geoid model a case study in Iran.},  J Geod, Vol. 79, pp. 540-551. 2005

\bibitem {hydro2006} \textsc{Lehner, B., Verdin, K., Jarvis, A.} , \textit{HydroSHEDS Technical Documentation}, Version 1.0, 2006.

\bibitem {Jarvis2008} \textsc{Jarvis, A., Guevara, E., Reuter, H. I., Nelson, A. D.} , \textit{Hole-filled SRTM for the globe : version 4}, 2008.

\bibitem {Li2009} \textsc{Li, J., Wong, D.} , \textit{Effects of DEM sources on hydrologic applications.}, Computers Environment and Urban Systems, p. 1-11. 2009

\bibitem {Masuelli2009} \textsc{Masuelli, S., Vazquez, P. Faure, O.} , \textit{Adecuación del DEM SRTM de 90 metros para usos Hidrológicos en llanuras} Remote Sensing and Space Information System, SELPER VOL. 28 Nº 1, 2009 

\bibitem {Matthews1975} \textsc{Matthews, B. W.} , \textit{Comparison of the predicted and observed secondary structure of T4 phage lysozyme}, Biochimica et Biophysica Acta (BBA) - Protein Structure. 405 (2): 442–451, 1975

\bibitem {miliaresis2009} \textsc{Miliaresis, G.; Delikaraoglou, D.} , \textit{Effects of percent tree canopy density and DEM misregistration on SRTM/DEM vegetation height estimates},  Remote Sens. 1, 36-49, 2009.

\bibitem {morenoDeLasHeras2012} \textsc{Moreno de las Heras, M., Saco, P., Willgoose, G. R.} , \textit{A comparison of SRTM V4 and ASTER GDEM for hydrological applications in low relief terrain}, Photogrammetric Engineering and Remote Sensing 78(7):757-766. 2012

\bibitem {petrie1990} \textsc{Petrie, G. and Kennie, T. J. M.} , \textit{Terrain Modelling in Surveying and Civil Engineering},  351 pages (London: Whittles Publishing Company. 1990.

\bibitem {Rasmussen2000} \textsc{Rasmussen, C. E.} , \textit{The Infinite Gaussian Mixture Model}, Advances in Neural Information Processing Systems 12 S.A. Solla, T.K. Leen and K.-R. Muller (eds.), pp. 554–560, MIT Press 2000

\bibitem {reuter2007} \textsc{Reuter, H. I., Nelson, A., Jarvis, A.} , \textit{An evaluation of void filling interpolation methods for SRTM data}, International Journal of Geographical Information Science, Vol. 21, No. 9, 983-1008, 2007.

\bibitem {rodriguez2006} \textsc{Rodriguez, E.; Morris, C.S.; Belz, J.E.} , \textit{A Global Assessment of the SRTM Performance.},  Photogramm. Eng. Remote Sens. 72, 249-261, 2006.

\bibitem {rozasVazquez2009} \textsc{Rozas Vásquez, D., Rebolledo Castro, G., Gutiérrez Zamorano, P.} , \textit{Evaluación de la Calidad de los DEM y SRTM y ASTER en una Cuenca Costera de la Región de la Araucanía, bajo distintas condiciones de Relieve y Cobertura Vegetal}, Laboratorio de Planificación Territorial, Escuela de Ciencias Ambientales, Facultad de Recursos Naturales, Universidad Católica de Temuco, Chile. 2009

\bibitem {Schumann2008} \textsc{Schumann, G., Matgen, P., Cutler, M.E.J., Black, A., Hoffmann, L., and Pfister, L.} , \textit{Comparison of remotely sensed wated stager from LiDAR, topographic contours and SRTM.}, Journal of Photogrammetry and Remote Sensing, Vol. 63, p.283-296. 2008

\bibitem {tachikawaGDEM22011} \textsc{Tachikawa, T., Kaku M., Iwasaki A.} , \textit{ASTER Global Digital Elevation Model Version 2 – Summary of Validation Results},  NASA Land Processes Distributed Active Archive Center and the Joint Japan-US ASTER Science Team 2011.

\bibitem {tachikawaGDEM22011} \textsc{Tomiyasu K.} , \textit{Conceptual performance of a satellite borne, wide swath synthetic aperture radar},  IEEE Transactions on Geoscience and Remote Sensing 108-116. 1981 (2). 

\bibitem {USGS2000} \textsc{USGS - U.S. Geological Survey} , \textit{HYDRO1k Elevation Derivative Database}, USGS EROS Data Center, Sioux Falls, SD. 2000. Available at http://edc.usgs.gov/products/elevation/gtopo30/hydro/


\bibitem {vazquez2007} \textsc{Vazquez, P., Masuelli, S., Platzeck, G., Boolsen, O.} , \textit{Mapa de riesgo hídrico}, XII Congreso de Teledetección de la Asociación Española de Teledetección, Mar del Plata, Argentina. 2007

\bibitem {OLITIRS} \textsc{USGS}, \textit{https://lta.cr.usgs.gov/L8C1HigherLevel}

\bibitem {dzetsaka} \textsc{DZETSAKA}, \textit{https://github.com/lennepkade/dzetsaka.} 2018

\bibitem {hydroShedsSite} \textsc{HydroSHEDS}, \textit{http://earlywarning.usgs.gov/hydrodata/sa\_15s\_zip\_grid/sa\_dem\_15s\_grid.zip}

\bibitem {earthExplorer} \textsc{EarthExplorer}, \textit{https://earthexplorer.usgs.gov/} 2018

\bibitem {nasa2003} \textsc{NASA} , \textit{SRTM Data Editing Rules}, Version 2.0. 23 pp USGS \\https://dds.cr.usgs.gov/srtm/version2\_1/Documentation/SRTM\_edit\_rules.pdf, 2003.


\end{thebibliography}
